Analyses of Promises in R

### 2018-03-26 analysis/report/01-lifespan.Rmd
Add interference analysis to report and miscellaneous improvements

show_table <- function(analysis_name, table_filename) {
    get_table(analysis_name, table_filename) %>%
    datatable(rownames = FALSE)
}
```

>>>>

show_table <- function(analysis_name, table_filename) {
    get_table(analysis_name, table_filename) %>%
    datatable(rownames = FALSE, options = list(scrollX = TRUE))
}
```
